---
title: ""
format: 
  html:
    css: styles.css
execute:
  echo: FALSE
  message: FALSE
  warning: FALSE
---
# What affects golf score the most?
#### By Zephan Shivam

<br>


```{r}
#| echo: FALSE
#| message: FALSE
library(tidyverse)
library(patchwork)
golf_data <- read_csv(file = "dg_new_course_table.csv") #Reading the data
```

<div class="plot-container">
```{r}
#| echo: FALSE
#| message: FALSE
#| fig.width: 8
#| fig.height: 5


#Plotting the combined graph
ggplot() + 
  geom_point(data = golf_data, aes(x = ott_sg, y = adj_score_to_par, color = "Off the Tee"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = ott_sg, y = adj_score_to_par, color = "Off the Tee"), method = "lm", se = FALSE) +
  geom_point(data = golf_data, aes(x = app_sg, y = adj_score_to_par, color = "Approach Shots"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = app_sg, y = adj_score_to_par, color = "Approach Shots"), method = "lm", se = FALSE) + 
  geom_point(data = golf_data, aes(x = arg_sg, y = adj_score_to_par, color = "Around the Green"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = arg_sg, y = adj_score_to_par, color = "Around the Green"), method = "lm", se = FALSE) + 
  geom_point(data = golf_data, aes(x = putt_sg, y = adj_score_to_par, color = "Putting"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = putt_sg, y = adj_score_to_par, color = "Putting"), method = "lm", se = FALSE) + 
  labs(title = "Relation between quality of different strokes and score", x = "Strokes Gained", y = "Score", color = "Strokes Gained") + 
  scale_color_manual(values = c("Off the Tee" = "blue", "Approach Shots" = "red", "Around the Green" = "green", "Putting" = "purple")) + theme_minimal() + theme(plot.title = element_text(face = "bold"))

```
</div>
#### Have you ever watched golf and wondered, "Sure, many things affect the score, but what affects it the most?" I sure have wondered that. So I created this project to answer that question. It takes data from datagolf.com, where all data is golf related, and analyzes what has the most effect on the score. In this project, we see that good putting on Par 3s and Par 4s seem to make the most difference on the score.
