---
title: ""
format: 
  html:
    css: styles.css
execute:
  echo: FALSE
  message: FALSE
  warning: FALSE
---
# What affects golf score the most?
#### By Zephan Shivam

<br>


```{r}
#| echo: FALSE
#| message: FALSE
library(tidyverse)
library(patchwork)
golf_data <- read_csv(file = "dg_new_course_table.csv") #Reading the data
```

```{r}
#| echo: FALSE
#| message: FALSE
#| fig.width: 8
#| fig.height: 5


#Plotting the combined graph
ggplot() + 
  geom_point(data = golf_data, aes(x = ott_sg, y = adj_score_to_par, color = "Off the Tee"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = ott_sg, y = adj_score_to_par, color = "Off the Tee"), method = "lm", se = FALSE) +
  geom_point(data = golf_data, aes(x = app_sg, y = adj_score_to_par, color = "Approach Shots"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = app_sg, y = adj_score_to_par, color = "Approach Shots"), method = "lm", se = FALSE) + 
  geom_point(data = golf_data, aes(x = arg_sg, y = adj_score_to_par, color = "Around the Green"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = arg_sg, y = adj_score_to_par, color = "Around the Green"), method = "lm", se = FALSE) + 
  geom_point(data = golf_data, aes(x = putt_sg, y = adj_score_to_par, color = "Putting"), alpha = 0.35) + 
  geom_smooth(data = golf_data, aes(x = putt_sg, y = adj_score_to_par, color = "Putting"), method = "lm", se = FALSE) + 
  labs(title = "Relation between different strokes and score", x = "Strokes Gained", y = "Score", color = "Strokes Gained") + 
  theme(plot.title = element_text(face = "bold")) +
  scale_color_manual(values = c("Off the Tee" = "blue", "Approach Shots" = "red", "Around the Green" = "green", "Putting" = "purple"))

```

#### Did you know that golfers only make birdies, on average, 15-25% of the time? Because of this difficulty, it is important to know what makes the most difference on the score. This project does just that, looking at many different variables and sees whether they have an effect on the score. In this project, we see that good putting on Par 3s and Par 4s seem to make the most difference on the score.
